WASP-4 is Accelerating Toward the Earth

### 2020-03-21 second_paper_review/response_20200320.txt

Dear Dr. Jackson,

We thank you for organizing the review of our paper, and also
thank the referee for their helpful comments.  We have
considered the referee's remarks carefully and revised our
manuscript accordingly.

Below, we have reproduced the relevant portions of the
referee's report, alongside our responses. A list of changes is
appended to the manuscript using the trackchanges AASTeX
macros.

Sincerely,

Luke Bouma

******************************************
REFEREE COMMENT
----------
Section 2.1, Paragraph 2.

It would be helpful if the authors briefly describe the exact
meaning of "high quality" in the context of the transit times
used in the analysis.

RESPONSE
----------
> Thank you for this prompt. We have removed the phrase "high
> quality", as its precise definition is not of particular
> importance for this study. It is defined in Section 3.4 of
> Baluev+ 2019, through an empirical cutoff that Baluev+ made
> based on the sampling cadence and the light-curve residual
> RMS.

******************************************
REFEREE COMMENT
----------
Section 3.1

In this section it is stated that the assumption of "a Gaussian
likelihood and sampling over the posterior probability
distributions" is made. This assumption needs further
justification given the variety of data sources included. In
particular, it is later stated in Section 3.1 that the cause of
the high reduced chi2 values "must be some additional signal or
noise". Alternatively, it could indeed mean that the Gaussian
likelihood assumption is not completely valid.

RESPONSE
----------
> We expect that the high reduced chi2 values are likely due to
> either underestimated statistical uncertainties on transit
> timing measurements, or that they are caused by systematic
> errors.  We do not think that the specific choice of a
> Gaussian likelihood vs. an alternate choice of likelihood is
> necessarily at issue.
>
> We made every effort to ensure the integrity of our included
> times, for instance by rejecting times that did not clearly
> specify the nature of the barycentric/heliocentric
> correction, or the nature of the leap-second correction (UTC
> vs TDB). However we ultimately need to trust timestamps that
> were recorded by observers other than ourselves.  Despite
> these efforts, some observations might have systematic errors
> (e.g., of order 1 minute for leap-second corrections), but we
> cannot be sure which ones.
>
> Our approach for dealing with this issue was to introduce a
> free parameter that uniformly inflates the uncertainties of
> derived parameters (e.g., dP/dt) by the factor that would
> ensure reduced chi2 = 1.  Any suggestions on better
> methodologies are welcome, however it is not clear to us that
> there is any way around the fundamental issue of needing to
> trust that observers can record time correctly.
>
> We have updated the wording in the manuscript to improve the
> clarity with which we present these issues.

******************************************
REFEREE COMMENT
----------
Section 3.3

The discussion and figure in this section are very good.
However, it is not sufficiently demonstrated that a stellar
companion is ruled out when considering the possible angular
separations of the companion resulting from being near inferior
or superior conjunction. This is particularly important for
this system since even a small degree of coplanarity of the
companion with WASP-4b would result in an edge on orbit that
makes the companion difficult to detect when near conjunction
locations. Also, the very last sentence of this section "Figure
4 shows the result." should describe the results of the figure
in more detail.

RESPONSE
----------
> We agree; we erroneously neglected this issue in the
> submitted manuscript.  Thank you for bringing it to our
> attention.
>
> In the revised manuscript, we amended our methodogy to
> probabilistically include the speckle imaging limits. The
> procedure is discussed in the text, but in brief, for each
> simulated companion (which has known orbital parameters), we
> calculated its projected separation on-sky at the time of the
> imaging observation. We then multiply the RV and speckle
> imaging posteriors, yielding contours in a revised Figure 4.
>
> This revision led to slightly weaker upper limits on the
> companion mass (200Mjup -> 300Mjup), but did not otherwise
> affect the primary conclusions of the study.
>
> The comment regarding the last sentence has also been
> addressed; thank you.

******************************************
REFEREE COMMENT
----------
Section 4.1

Paragraph 1. The paragraph implies that the Doppler effect is
the sole cause of the timing derivative. However, and given the
2 sigma discrepancy, the wording should allow for the
possibility that the timing derivative is actually a result of
a combination of the described effects.

RESPONSE
----------
> We have modified the wording in this paragraph to clarify
> that this is a possibility, but that at present the dominant
> physical effect is the line-of-sight acceleration.

******************************************
REFEREE COMMENT
----------
Section 4.2

Paragraph 3. "hot Jupiters is expected" should be "hot Jupiters
are expected".

RESPONSE
----------
> Corrected, thank you.

### 2020-03-25 second_paper_review/response_20200320.txt

RESPONSE
----------
> Thank you for this prompt. We have removed the phrase "high
> quality", as its precise definition is not of particular
> importance for this study. It is defined in Section 3.4 of
> Baluev+ 2019, through an empirical cutoff that Baluev+ made
> based on the sampling cadence and the light-curve residual
> RMS.

******************************************
REFEREE COMMENT
----------
Section 3.1

In this section it is stated that the assumption of "a Gaussian
likelihood and sampling over the posterior probability
distributions" is made. This assumption needs further
justification given the variety of data sources included. In
particular, it is later stated in Section 3.1 that the cause of
the high reduced chi2 values "must be some additional signal or
noise". Alternatively, it could indeed mean that the Gaussian
likelihood assumption is not completely valid.

RESPONSE
----------
> We expect that the high reduced chi2 values are due to
> underestimated statistical uncertainties on transit
> timing measurements, or systematic errors due to stellar
> activity or mistakes in the conversion to the standard
> time system.  We do not think that the specific choice of a
> Gaussian likelihood vs. an alternate choice of likelihood is
> necessarily at issue.
>
> We made every effort to ensure the integrity of our included
> times, for instance by rejecting times that did not clearly
> specify the nature of the barycentric/heliocentric
> correction, or the nature of the leap-second correction (UTC
> vs TDB). However we ultimately need to trust timestamps that
> were recorded by observers other than ourselves.  Despite
> these efforts, some observations might have systematic errors
> (e.g., of order 1 minute for leap-second corrections), but we
> cannot be sure which ones.
>
> Our approach for dealing with this issue was to introduce a
> free parameter that uniformly inflates the uncertainties of
> derived parameters (e.g., dP/dt) by the factor that would
> ensure reduced chi2 = 1.  This seems like the simplest and most
> reasonable way to handle this heterogeneous dataset.
>
> We have updated the wording in the manuscript to improve the
> clarity with which we present these issues.

@@

******************************************
REFEREE COMMENT
----------
Section 3.3

The discussion and figure in this section are very good.
However, it is not sufficiently demonstrated that a stellar
companion is ruled out when considering the possible angular
separations of the companion resulting from being near inferior
or superior conjunction. This is particularly important for
this system since even a small degree of coplanarity of the
companion with WASP-4b would result in an edge on orbit that
makes the companion difficult to detect when near conjunction
locations. Also, the very last sentence of this section "Figure
4 shows the result." should describe the results of the figure
in more detail.

RESPONSE
----------
> We agree; we erroneously neglected this issue in the
> submitted manuscript.  Thank you for bringing it to our
> attention.
>
> In the revised manuscript, we amended our methodology to
> probabilistically include the speckle imaging limits. The
> procedure is discussed in the text, but in brief, for each
> simulated companion (which has known orbital parameters), we
> calculated its projected separation on-sky at the time of the
> imaging observation. We then multiply the RV and speckle
> imaging posteriors, yielding contours in a revised Figure 4.
>
> This revision led to slightly weaker upper limits on the
> companion mass (200Mjup -> 300Mjup), but did not otherwise
> affect the primary conclusions of the study.
>
> The comment regarding the last sentence has also been
> addressed; thank you.

### 2020-03-26 paper/ms.tex
fix sentence

From the high values of $\chi^2_{\rm red}$, we can surmise that
neither model provides a satisfactory fit to the transit data; there
must be some additional signal or noise.  The earlier study by
\citetalias{bouma_wasp4b_2019} found that the quadratic model for the
(sparser) transit data gave $\chi^2_{\rm red}=1.0$.  The worsening of
$\chi^2_{\rm red}$ \replaced{probably reflects}{could reflect}
underestimated \replaced{measurement}{statistical} uncertainties in at
least some of the newly reported transit times, \added{perhaps} due to
time correlated noise in the photometry. It might also be due to
\replaced{errors or}{systematic} misunderstandings of the time systems
in which the data were recorded, despite our best efforts to interpret
the literature. \added{In particular, mistaken leap-second corrections
can introduce systematic errors of order one minute.}  \replaced{In
what follows,}{Since we have no way of identifying which observations
are affected by these issues,} we opted to \added{uniformly} enlarge
the uncertainties in the best-fitting parameters of each model by a
factor of $(\chi^2_{\rm red})^{1/2}$.  This was a factor of
$\approx$1.73$\times$ for the linear model, and $\approx$1.41$\times$
for the quadratic model.

>>>>

From the high values of $\chi^2_{\rm red}$, we can surmise that
neither model provides a satisfactory fit to the transit data; there
must be some additional signal or noise.  The earlier study by
\citetalias{bouma_wasp4b_2019} found that the quadratic model for the
(sparser) transit data gave $\chi^2_{\rm red}=1.0$.  The worsening of
$\chi^2_{\rm red}$ \replaced{probably reflects}{could reflect}
underestimated \replaced{measurement}{statistical} uncertainties in at
least some of the newly reported transit times\deleted{, due to
time correlated noise in the photometry}. It might also be due to
\replaced{errors or}{systematic} misunderstandings of the time systems
in which the data were recorded, despite our best efforts to interpret
the literature. \added{In particular, mistaken leap-second corrections
can introduce systematic errors of order one minute.}  \replaced{In
what follows,}{Since we have no way of identifying which observations
are affected by these issues,} we opted to \added{uniformly} enlarge
the uncertainties in the best-fitting parameters of each model by a
factor of $(\chi^2_{\rm red})^{1/2}$.  This was a factor of
$\approx$1.73$\times$ for the linear model, and $\approx$1.41$\times$
for the quadratic model.
